Computing environment

### 2023-05-05 analysis/environment.qmd
Add quarto version

```{r get-session-info}
#| class-output: text
# Injecting Stan info into the platform info adapted from TJ Mahr:
# https://github.com/tjmahr/tjmahr.github.io/commit/b8be089
session_info <- sessioninfo::session_info()
session_info$platform$`stan (cmdstanr)` <- cmdstanr::cmdstan_version()

>>>>

```{r get-session-info}
#| class-output: text
# Injecting Stan info into the platform info adapted from TJ Mahr:
# https://github.com/tjmahr/tjmahr.github.io/commit/b8be089
session_info <- sessioninfo::session_info()
session_info$platform$`quarto` <- as.character(quarto::quarto_version())
session_info$platform$`stan (cmdstanr)` <- cmdstanr::cmdstan_version()
